Technical Note: Measurement of nuclear fuel assembly's bow from visual inspection's video record

### 2022-12-19 article-with-bib.tex
Grammarly check

Once the $\alpha^{real}_f$ are computed for $\forall f \in F$ we have to transform an angle value into frame a horizontal shift. For this purpose we use simple trigonometry:
$$
cos(\alpha_f^{real}) = \frac{\Delta x}{h_f},
$$
where $\alpha_f^{real}$ is frame real angle, $\Delta x$ is horizontal frame shift and $h_f$ is an effective frame height. The effective frame height depends on camera speed and camera frame rate and corresponds to number of vertical pixels by which are shifted two consecutive video frames.

Because this step acummulates the error across the video sequence, we recommend to add a procedure for double verification of computed values. The horizontal shift can be estimated also a different way. In our calibration method we use a computation of $\Delta x$ directly from image data. This is done by convolution which minimizes this term:

@@

Where $I_{f_1}$ and $I_{f_2}$ are intensities of pixels in frames $f_1$ and $f_2$ and $W$, $H$ denotes width and height of the video frames. In other words, we try to find out best position of bottom row of $f_1$ and top row of $f_2$. For this minimization we took frames for which bottom and top rows corresponds (i.e. their distance in video sequence is e.g. 60 frames - according to the camera speed).

>>>>

Once the $\alpha^{real}_f$ are computed for $\forall f \in F$ we have to transform an angle value into a frame horizontal shift. For this purpose, we use simple trigonometry:
$$
cos(\alpha_f^{real}) = \frac{\Delta x}{h_f},
$$
where $\alpha_f^{real}$ is frame real angle, $\Delta x$ is horizontal frame shift and $h_f$ is an effective frame height. The effective frame height depends on camera speed and frame rate and corresponds to number of vertical pixels by which two consecutive video frames are shifted.

Because this step acummulates the error across the video sequence, we recommend to add a procedure for double verification of computed values. The horizontal shift can also be estimated by another way. In our calibration method, we use a computation of $\Delta x$ directly from image data by minimization of this  convolution term:

@@

Where $I_{f_1}$ and $I_{f_2}$ are intensities of pixels in frames $f_1$ and $f_2$ and $W$, $H$ denotes width and height of the video frames. In other words, we try to findout best position of bottom row of $f_1$ and top row of $f_2$. For this minimization we took frames for which bottom and top rows corresponds (i.e., their distance in video sequence is (e.g.) 60 frames - according to the camera speed).
